Supplementary Material

### 2022-02-27 analysis/supplementary-materials/supp-mat.Rmd
update supp mat

---
title: "Supplementary Material"
output:
  html_document:
    keep_md: yes
    df_print: paged
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
    df_print: kable
---

@@

## R Session info

@@

@@

## Raw data

The raw data can be downloaded from GitHub:

```sh
# solution counts
wget https://github.com/bbartholdy/byoc-starch/blob/main/analysis/data/raw_data/solution_counts.csv

# sample counts
wget https://github.com/bbartholdy/byoc-starch/blob/main/analysis/data/raw_data/starch_counts.csv
```

Raw counts from the treatment solutions before extrapolation.

```{r raw-data-sol, echo=FALSE}
sol_counts
```

Raw counts from the calculus samples before extrapolation:

```{r raw-data-samp, echo=FALSE}
raw_counts
```

## Experimental setup

```{r plate-lid-1, fig.cap="The 24 deepwell plate and the lid with pegs (substrata)"}
knitr::include_graphics(here("analysis/figures/plate_lid_side.jpg"))
```

```{r plate-lid-2, fig.cap="The 24 deepwell plate with the lid (almost) on."}
knitr::include_graphics(here("analysis/figures/plate_lid_on.jpg"))
```

## Protocols

## Microscope images

```{r img-1, echo=FALSE, fig.cap="Image of starch granules extracted from a potato treatment sample"}
knitr::include_graphics(here("analysis/figures/starches_w_bar.jpg"))
```

```{r img-2}
knitr::include_graphics(here("analysis/figures/SNAP-103412-0006.jpg"))
```

```{r img-3, fig.cap="Microscope image of wheat starch from a wheat treatment sample."}
knitr::include_graphics(here("analysis/figures/SNAP-164650-0012.jpg"))
```

## Amylase activity

Amylase activity in U/mL enzyme, where U is mg maltose released from starch in six minutes at 36 &deg;C.

@@

```{r amylase-activity-tables}
plt1_ph1_result # plate 1, photometric reading 1
plt1_ph2_result # plate 1, photometric reading 2
plt2_ph1_result # plate 2, photometric reading 1
plt2_ph2_result # plate 2, photometric reading 2
```

## Control samples

@@

## Count corrections

@@

## Some additional plots

@@

### ...and a table

>>>>

---
title: "Supplementary Material"
output:
  bookdown::html_document2:
    df_print: paged
    toc: yes
    toc_float: yes
  bookdown::pdf_document2:
    toc: yes
    df_print: kable
---

@@

# R Session info

@@

# Experimental setup

```{r plate-lid-1, fig.cap="The 24 deepwell plate and the lid with pegs (substrata)"}
knitr::include_graphics(here("analysis/supplementary-materials/figures/plate_lid_side.jpg"))
```

```{r plate-lid-2, fig.cap="The 24 deepwell plate with the lid (almost) on."}
knitr::include_graphics(here("analysis/supplementary-materials/figures/plate_lid_on.jpg"))
```

# Protocols

# Raw data

The raw data can be downloaded from OSF:

Solution counts: <https://osf.io/kz3b2/>  
Sample counts: <https://osf.io/kz3b2/>

```sh
# solution counts
wget https://osf.io/kz3b2/download -O solution_counts.csv

# sample counts
wget https://osf.io/kz3b2/download -O starch_counts.csv
```

@@

# Microscope images

```{r img-1, echo=FALSE, fig.cap="Image of starch granules extracted from a potato treatment sample"}
knitr::include_graphics(here("analysis/supplementary-materials/figures/starches_w_bar.jpg"))
```

```{r img-2}
knitr::include_graphics(here("analysis/supplementary-materials/figures/SNAP-103412-0006.jpg"))
```

```{r img-3, fig.cap="Microscope image of wheat starch from a wheat treatment sample."}
knitr::include_graphics(here("analysis/supplementary-materials/figures/SNAP-164650-0012.jpg"))
```

# Amylase activity

Amylase activity in U/mL enzyme, where U is the amount of enzyme needed to
release 1 $\mu$mole maltose from starch in six minutes at 36 &deg;C.

@@

```{r amylase-plt1-read1}
plt1_ph1_result %>%
  knitr::kable("Amylase activity in U/mL for plate 1, photometric read 1.")
```

```{r amylase-plt1-read2}
plt1_ph2_result %>%
  knitr::kable("Amylase activity in U/mL for plate 1, photometric read 2.")
```

```{r amylase-plt2-read1}
plt2_ph1_result %>%
  knitr::kable("Amylase activity in U/mL for plate 2, photometric read 1.")
```

```{r amylase-plt2-read2}
plt2_ph2_result %>%
  knitr::kable("Amylase activity in U/mL for plate 2, photometric read 2.")
```

# Control samples

@@

# Count corrections

@@

# Some additional plots

@@

## ...and a table
